A generalization of the Bradley-Terry model for draws in chess

### 2019-05-27 inst/collusion_chess_draws.Rnw
typos

The present work details an approach to chess analysis based on
reification of entities representing propensity to draw, and the
first-mover (or white player) advantage.  Likelihood functions for the
players' and reified entities' strengths are defined using only
specific tournament outcomes; further, the analysis uses only game
outcome, not length.

@@

\cite{moul2009} present detailed Monte Carlo simulations
to assess the likely impact of any Soviet cartel on tournament outcomes.
In principle, the present system of likelihood and reified entities
would admit such simulations and might be interesting to compare results.

>>>>

The present work details an approach to chess analysis based on
reification of entities representing propensity to draw, and the
first-mover (or white player) advantage.  Likelihood functions for the
players' and reified entities' strengths are defined using only
specific tournament outcomes; further, the analysis uses only game
outcome, not length.  Many hypotheses of interest to the chess
community may be analysed straightforwardly.

@@

\cite{moul2009} present detailed Monte Carlo simulations
to assess the likely impact of any Soviet cartel on tournament outcomes.
In principle, the present system of likelihood and reified entities
would admit such simulations and it might be interesting to compare results.
